---
title: "Week1_Homework"
author: "2162398"
date: "2022-10-09"
output:
  pdf_document: 
    latex_engine: xelatex
---

**Part 2** 

**2.1** Create variables, x, a, and b:

```{r}
x=12
a=2
b=4
```

Based on this, give R assignment statements that set the variable z to:

**2.1.1**

```{r}
z=x**(a**b)
z
```

**2.1.2**

```{r}
z=(x**a)**b
z
```

**2.1.3**

```{r}
z=3*(x**3)+2*(x**2)+6*x+1
z
```

**2.1.4**

```{r}
z=z+1
z
```

**2.2** Give R expressions that return the following vectors
#1. (1,2,3,4,5,6,7,8,7,6,5,4,3,2,1)
#2. (1,2,2,3,3,3,4,4,4,4,5,5,5,5,5)

**2.2.1**

```{r}
X=c(1:8,7:1)
X
```

**2.2.2**

```{r}
Y=rep(1:5,times=c(1,2,3,4,5))
Y
```

**2.3** Find the number from 1 to 100 that is not divisible by 2、3 or 7

```{r}
a=c()
H=c(1:100)
for (i in H){
  if(i%%2!=0 &i%%3!=0 &i%%7!=0){
    a=c(a,i)
    
    
    
  }
}
print(a)
```

**2.4** Suppose that queue \<- c("Steve", "Russell", "Alison", "Liam") and that queue represents a super- market queue with Steve first in line. Using R expressions update the supermarket queue as successively:

```{r}
queue = c("Steve", "Russell", "Alison", "Liam") 
```

**2.4.1** Barry arrives;

```{r}
queue=append(queue,"Barry")
queue
```

**2.4.2** Steve is served;

```{r}
queue=queue[-1]
queue
```

**2.4.3** Pam talks her way to the front with one item;

```{r}
queue=append(queue,"Pam", after=0)
queue
```

**2.4.4** Barry gets impatient and leaves;

```{r}
queue=queue[-which(queue=="Barry")]
queue
```

**2.4.5** Alison gets impatient and leaves.

```{r}
queue=queue[-which(queue=="Alison")]
queue
```

**2.4.6** Using the function which(x), find the position of Russell in the queue.

```{r}
a=which(queue=="Russell")
a
```

**Part 3**

```{r}
# Install & Library R package carData.
install.packages("carData",repos = "http://cran.us.r-project.org")
library(carData)
#install "dplyr' packages
install.packages("dplyr",repos = "http://cran.us.r-project.org")
library('dplyr')

```

3.1

```{r}
#How many rows and how many columns does Salaries have? 397 rows 6 columns
dim(Salaries)
```

3.2
```{r}
#3.2 How many columns are numerical, how many columns contain factors? 3 factors columns 3 int columns
group_by(Salaries)
```

3.3

```{r}
#3.3  Create a new data.frame, salaries_a, that only contains the data from discipline = "A". How many rows does this data.frame have? Check the documentation, what does discipline = "A" stand for? 181 rows
salaries_a=data.frame(filter(Salaries,discipline=="A"))
nrow(salaries_a)
```

3.4

```{r}
#Create a new data.frame, salaries_f, that only contains the data from the Female professor at a  ROWS rank of AssocProf. How many of those are in discipline A, how many in discipline B? A:4 B:6
salaries_f= data.frame(filter(Salaries,sex=="Female" & rank=="AssocProf"))
sum(salaries_f$discipline=="A")
sum(salaries_f$discipline=="B")
```

3.5

```{r}
#What is the percentage of professors that started this year (yrs.service == 0)?

salaries_0year=data.frame(filter(Salaries,yrs.service==0))
nrow(salaries_0year)/nrow(Salaries)
```

3.6

```{r}
#How many professors in discipline A have been professor for more than 10 years (i.e., yrs.service larger than 10)? 119 people
salaries_10y_A=data.frame(filter(salaries_a,yrs.service>10))
nrow(salaries_10y_A)
```

3.7

```{r}
#3.7 Add a new column called luck to Salaries and fill it with random samples from the integers 1 to 6.
Salaries[ , 'luck'] = (sample(1:6,nrow(Salaries),replace = T))
head(Salaries)
```

3.8

```{r}
#3.8 How many of the Associate Professors (i.e., rank of AssocProf) got lucky (i.e., have a 6 in column luck)? What percentage of the Associate Professors got lucky? 
salaries_asst=data.frame(filter(Salaries,rank=="AsstProf"))
salaries_luck_asst=data.frame(filter(salaries_asst,luck==6))
nrow(salaries_luck_asst)/nrow(salaries_asst)

```
